Kernel Development Using Rust: A Systematic Literature Review

### 2024-05-20 paper.tex
Update on Overleaf.

We search all three databases with the keywords listed in table~\ref{tab:keywords} between January
1, 2019 and April 1, 2024. While both ACM and IEEE had mutually exclusive results Scopus had 44
duplicates that needed to be removed. We then used Google Scholar for forward and backward
snowballing.

@@

\subsection{RQ1}

@@

Lankes et al.~\cite{Lankes2019-cm} detailed their experiences with developing a Unikernel in
Rust. Originally written in C and called HermitCore the authors ported the Kernel to the Rust
programming language in order to take advantage of Rust's memory safe features. The new Unikernel
consists of only 3.27\% unsafe Rust with the rest of the code base consisting of safe Rust

\subsection{RQ2}

@@

\subsection{RQ3}

@@

\begin{itemize}

\item Deeply ingrained monomorphization
\item Suboptimal compiler generated support code
\item Hidden data structures and data
\item Fewer compiler optimizations
\end{itemize}

@@

\begin{table}
  \begin{tabular}{||c|c||}
    \hline
    System Type & Papers\\
    \hline\hline
    Embedded & ~\cite{Ayers2022-vk} \\
    Non-Embedded & 0 \\
    Unikernel & 0 \\
    Kernel & 0 \\
    \hline
  \end{tabular}
\end{table}

This is a list of operating systems.
\begin{itemize}
\item \href{https://docs.kernel.org/rust/}{Linux kernel v6.1+}
\item \href{https://github.com/tock/tock}{Tock}
\item \href{https://hubris.oxide.computer/}{Hubris OS}
\item Theseus (Mono)
\item Redleaf
\item Splinter
\item Redox
\item Drone OS
\item Bern RTOS
\item Hermit (unikernel)
  \item Atmoshpere (Micro)
\end{itemize}

>>>>

We search all three databases with the keywords listed in table~\ref{tab:keywords} between January
1, 2019 and April 1, 2024. While both ACM and IEEE had mutually exclusive results Scopus had 44
duplicates that needed to be removed. We then used Google Scholar for forward and backward
snowballing. We choose to look at only the previous 5 years of research in order to capture the bleeding edge research that is currently being done.

@@

\subsection{RQ1 What are the existing approaches and methodologies for implementing
      operating system kernels in Rust?}

Table~\ref{tab:RQ1} summarizes our findings regarding what existing approaches researchers are using to integrate rust into the kernel.

@@

Lankes et al.~\cite{Lankes2019-cm} detailed their experiences with developing a Unikernel in
Rust. Originally written in C and called HermitCore the authors ported the Kernel to the Rust
programming language in order to take advantage of Rust's memory safe features. The new Unikernel
consists of only 3.27\% unsafe Rust with the rest of the code base consisting of safe Rust.

\begin{table*}
    \begin{tabular}{||p{2cm}|p{2cm}|p{8cm}||}
    \hline
    Approach & Papers & Operating System\\
    \hline\hline
    Monolithic  & ~\cite{The_kernel_development_community_undated-iw} & \href{https://docs.kernel.org/rust/}{Linux kernel v6.1+}\\
    Micro-kernel & ~\cite{Chen2023-wb} & Atmosphere, Redox, Redleaf\\
    Embedded & ~\cite{Culic2022-bk} & \href{https://github.com/tock/tock}{Tock} \\
    Unikernel & ~\cite{Lankes2019-cm} & RustyHermit \\
    Prototype & ~\cite{Boos2020-zh, Ijaz2023-da} & Thesus \\
    \hline
  \end{tabular}
  \caption{Approaches and Methodologies for Rust in the Kernel}
    \label{tab:RQ1}
\end{table*}

This is a list of operating systems.
\begin{itemize}
\item 
\item 
\item \href{https://hubris.oxide.computer/}{Hubris OS}
\item Theseus (Mono)

\item Splinter

\item Drone OS
\item Bern RTOS

\end{itemize}

\subsection{RQ2  What are the performance implications of using Rust for operating system
      kernel development in terms of throughput, latency, and resource utilization?}

@@

\subsection{RQ3 What are the major challenges, limitations, and lessons learned when
      developing operating system kernels in Rust, particularly in comparison to other languages?}

@@

\begin{itemize}
    \item Deeply ingrained monomorphization
    \item Suboptimal compiler generated support code
    \item Hidden data structures and data
    \item Fewer compiler optimizations
\end{itemize}

@@
